[![](./images/lindens.jpg)](https://en.wikipedia.org/wiki/Tilia) An Application of LIME to a Random Forest

### 2019-02-28 presentations/graphics group/An Application of LIME to a Random Forest.Rmd
finished first section of talk

.pull-left[
### Goals for the talk
- Explain the LIME algorithm
- Present an application of LIME
- Highlight problems with this application

### The plan

@@

# Idea of the LIME Procedure

@@

| | Feature 1 | <span style="color:blue">Feature 2</span> | <span style="color:blue">Feature 3</span> | Feature 4 | Similarity Score | Prediction |
| --: | :--: | :--: | :--: | :--: | :--: | :--: |
| test observation | 2 | 4 | 2 | 10 | exact | $\hat{y}_{\mbox{obs}}$ |
| perturbation 1 | 2 | 3 | 2 | 12 | very close | $\hat{y}_1$ |
| $\vdots$ | $\vdots$ | ... | ... | ... | ... | 
| perturbation 5000  | 10 | 0 | 13 | 22 | not close | $\hat{y}_{5000}$ |

@@

.pull-left[
```{r eval = FALSE}
#install.packages("lime")
library(lime)
?lime
?explain
```
]

.pull-right[![](./images/lime.png)]
---

>>>>

.pull-left[
### The plan

@@

# Generalized Version of the LIME Procedure

@@

| | Feature 1 | <span style="color:blue">Feature 2</span> | <span style="color:blue">Feature 3</span> | Feature 4 | Similarity Score | <span style="color:blue">Prediction</span>|
| --: | :--: | :--: | :--: | :--: | :--: | :--: |
| test observation | 2 | 4 | 2 | 10 | exact | $\hat{y}_{\mbox{obs}}$ |
| perturbation 1 | 2 | 3 | 2 | 12 | very close | $\hat{y}_1$ |
| $\vdots$ | $\vdots$ | ... | ... | ... | ... | 
| perturbation 5000  | 10 | 0 | 13 | 22 | not close | $\hat{y}_{5000}$ |

@@

![](./images/lime.png)

### Key Functions in the lime R package

```{r eval = FALSE}
#install.packages("lime")
library(lime)
?lime
?explain
```
